---
title: "Graphics_Analysis, MarkDown 4"
author: "Julie Norman"
date: "8/2/2017"
output: html_document
---

```{r}
library(ggplot2)
library(MASS)
library(tidyr)
library(readr)
library(tidytext)
library(tidyverse)
library(sotu)
library(lubridate)
library(tseries)
```


```{r}
sotu_df2 <- read_csv("DFExport4.csv")
all_data <- read_csv("DFExport4.csv")



```



## Outlier Deletion

```{r}
data_outlier <- all_data %>% 
  filter(year.x != 1981)



data_outlier[which(data_outlier$sotu_date == "1939-01-04"), "Bus_cycle"] = -0.377884616

NROW(data_outlier)
str(data_outlier)
```

## Score over time


lowess/loess parameter in ggplot for geom_smooth?

```{r}
ggplot(data_outlier, aes(x = sotu_date, y = net_score)) +
  geom_point() +
  geom_smooth(method = 'loess', span = .1)
```

```{r}
ggplot(data_outlier, aes(x = sotu_date, y = net_score)) +
  geom_line()
```

```{r}
ggplot(data_outlier, aes(x = sotu_date, y = Bus_cycle)) +
  geom_point() +
  geom_smooth(method = 'loess', span = .1)
```

#Business Cycle

```{r}
data_1850 <- data_outlier %>%
  filter(year.x >= 1850 & year.x <= 2009)

ggplot(data_1850, aes(x = net_score, y = Bus_cycle)) +
  geom_point()
```




## Info

Cross Correlation function 

```{r}
bus_ccf <- ccf(data_1850$Bus_cycle, data_1850$net_score) 

plot(bus_ccf, main = "Business Cycle and Net Sentiment")
```
the acf lag plot shows no association


# Recssion

```{r}
data_1854 <- data_outlier %>%
  filter(year.x >= 1854)

ggplot(data_1854, aes(x = net_score, y = recession)) +
  geom_point()
```



```{r}
ccf(data_1854$recession, data_1854$net_score) 

```

# Gini 

```{r}
data_1947 <- data_outlier %>%
  filter(year.x >= 1947 & year.x <= 2015)


ggplot(data_1947, aes(x = net_score, y = Gini)) +
  geom_point() 

```



```{r}

ccf(data_1947$Gini, data_1947$net_score)
```



# Gross National Income Median

```{r}
data_1948 <- data_outlier %>%
  filter(year.x >= 1948 & year.x <= 2016)

ggplot(data_1948, aes(x = net_score, y = GNI_med)) +
  geom_point()
```

```{r}
ccf(data_1948$GNI_med, data_1948$net_score)
```

#Gross National Income Average

```{r}
ggplot(data_1948, aes(x = net_score, y = GNI_avg)) +
  geom_point()
```

```{r}
GNI_avg <- data_1948$GNI_avg
net_score <- data_1948$net_score
GNI_lm <- lm(GNI_avg ~ net_score)

#plot(net_score, GNI_avg)
#abline(GNI_lm)
#summary(GNI_lm)
```


```{r}
ccf(data_1948$GNI_avg, data_1948$net_score)
```

# Percent Unemployment

```{r}
data_1949 <- data_outlier %>%
  filter(year.x >= 1949 & year.x <= 2016)

ggplot(data_1949, aes(x = net_score, y = pct_employ)) +
  geom_point()
```

```{r}

ccf(data_1949$pct_employ, data_1949$net_score)
```

# NDI Median

```{r}
ggplot(data_outlier, aes(x = NDI_med, y = net_score)) +
  geom_point() 
  
```

```{r}
ccf(data_1949$NDI_med, data_1949$net_score)
```

```{r}
NDI_med <- data_1948$NDI_med
net_score <- data_1948$net_score
NDImed_lm <- lm(NDI_med ~ net_score)

plot(net_score, NDI_med)
abline(NDImed_lm)
summary(NDImed_lm)
```

# NDI Average

```{r}
ggplot(data_outlier, aes(x = NDI_avg, y = net_score)) +
  geom_point() 
  
```

```{r}
ccf(data_1949$NDI_avg, data_1949$net_score)
```



```{r}
NDI_avg <- data_1948$NDI_avg
net_score <- data_1948$net_score
NDIav_lm <- lm(NDI_med ~ net_score)

plot(net_score, NDI_avg)
abline(NDIav_lm)
summary(NDIav_lm)
  
```

```{r}
ccf(data_1949$NDI_med, data_1949$net_score)
```


## President Age vs Sentiment Score

```{r}
qplot(age, net_score, data = all_data)
```

## War vs Ideology

```{r}
ggplot(all_data, aes(fill = va_wars, x = relative_ideology)) +
    geom_bar(position = "dodge")
```

## Net sentiment by Ideology

```{r}
ggplot(all_data, aes(y = net_score, x = relative_ideology)) +
  geom_boxplot()
```

```{r}
ggplot(all_data, aes(x = net_score)) +
  geom_histogram() +
  facet_grid(relative_ideology ~.)
```

```{r}
ggplot(data_outlier, aes(x = net_score, y = ..density..)) +
  geom_histogram(binwidth = 50, boundary = 0) +
  facet_grid(va_wars ~.)
```



### Time Series No Outlier

```{r}
qplot(sotu_date, net_score, data = data_outlier)
```


## Business Cycle vs Net Sentiment

```{r}
sotu_buscyc_df <- data_outlier[-c(1, 2, 3, 4, 5, 6, 7, 8, 9), ]

count(sotu_buscyc_df)

```


```{r}

Bus_cycle <- sotu_buscyc_df$Bus_cycle

count(sotu_buscyc_df$net_score)

plot(net_score, Bus_cycle, data = sotu_buscyc_df)
```

## Gini

```{r}

```




## Correlation Coefficient 


```{r}
recession = sotu_buscyc_df$recession
net_score = sotu_buscyc_df$net_score

cor(recession, net_score)
```






```{r}
gini_lm <- lm(data_1947$Gini ~ data_1947$net_score)
plot(data_1947$net_score, data_1947$Gini)
abline(gini_lm)
```






